Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalnew\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-18 ms.tex
small changes from a careful readthrough

\author{%
% The Heavy Lifters
Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
Timothy~D.~Morton\altaffilmark{\princeton},
Daniel~Foreman-Mackey\altaffilmark{\nyu,\cds},
% The Benefactors
John~Asher~Johnson\altaffilmark{\cfa},
David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
% The Observers
% (ranked by integration time x collecting area)
Brendan~P.~Bowler\altaffilmark{\caltech, \jcpa},
David~W.~Latham\altaffilmark{\cfa},
Allyson~Bieryla\altaffilmark{\cfa},
Andrew~W.~Mann\altaffilmark{\texas, \hjs},
}

@@

\begin{abstract}
The extended \kep\ mission, \KT, is now providing photometry of new fields every
three months in a search for transiting planets.
In a recent study, Foreman-Mackey and collaborators presented a list of 36 planet
candidates orbiting 31 stars in \KT\ \Ci.
In this contribution, we present stellar and planetary properties for all systems.
We combine ground-based seeing-limited survey data and
adaptive optics imaging with an automated transit analysis scheme to validate
\Nvalidated\ candidates as planets, \Nvalnew\ for the first time,
and identify \Nfp\ candidates as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \change{$2.24 \pm 0.25$ $R_\oplus$} planet with $T_{eq} = 271 \pm 16$ K and an
orbital period of 33 days.
We also present two new open-source software packages that enabled this analysis:
\texttt{isochrones}, a flexible tool for fitting theoretical stellar
models to observational data to determine stellar properties, and
\texttt{vespa}, a new general-purpose procedure to calculate false positive probabilities
and statistically validate transiting exoplanets.
\end{abstract}

@@

\section{Introduction}
The \kep\ telescope \citep{Borucki10} has led to a revolution in stellar and planetary
astrophysics, with 7305 ``objects of interest'' and 4173 ``planet candidates''
discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
The fidelity of this sample is high: most of these planet candidates are truly planets
\citep{Morton11b, Fressin13, Desert15}.
The mechanical failure of two reaction wheels on the spacecraft led to a repurposing
of the spacecraft into the \KT\ mission, in which the telescope points at
fields near the ecliptic plane for $\sim 75$ days at a time \citep{Howell14}.
In this observing strategy, two axes of motion of the spacecraft are
controlled by the two remaining reaction wheels, while the roll of the
spacecraft is balanced with solar radiation pressure and quasiperiodic
thruster firing.
As a result, the detector drifts relative to the sky
at the rate of $\sim 1\arcsec$ hr$^{-1}$, with rapid corrections due to thruster fires
approximately once every six hours.
Over the full duration of each campaign, the targets appear to remain near the
same location on the detector but both the slow drift and the corrections are
observable by eye \citep{Barentsen15}.

@@

\change{During the sampling process, we fit for galactic
extinction as one of our physical parameters.
For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
along that line of sight from the NASA/IPAC Extragalactic Database (NED), which reports the 
\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
COBE/DIRBE and IRAS/ISSA. 
The NED database returns the extinction in all relevant bandpasses except those used by
WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
We include the WISE bandpasses by applying the relative extinction values between 
SDSS, 2MASS, and WISE calculated by \citep{Davenport14}.
In each step of our fitting process, we draw an $A_V$, calculate the expected extinction
in all bandpasses $A_X$, and then measure the likelihood of our model stellar fit to the 
observed apparent magnitudes.
We apply a uniform prior ranging from zero to the obtained maximum extinction value and
marginalize over extinction in our final determination of stellar parameters. }

@@

\change{As our stellar results are model-dependent, we caution users who intend to use these 
parameters for other works, such as exoplanet population studies. When available, 
stellar parameters inferred through other techniques such as asteroseismology or 
spectroscopy should supersede these values. 
The observed photometric parameters  then consistent with spectroscopically-derived
parameters for stars with published spectra, and consistent with typical
model-dependent uncertainties
from photometric data \citep[e.g.][]{Huber14}.
We provide full samples of our posteriors on the physical parameters for each 
star\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}.}

\change{\citet{Bastien14} use observations of stellar ``flicker'' to suggest that 
approximately 50 percent of planet host stars have evolved off the
main sequence onto the subgiant branch, so that both the host stars and their 
planets are larger than previously reported. 
Similarly, in \KT\ \Ci\ we may expect to find evolved stars in a sample of planet
candidates. 
Indeed, we find this to be the case.
Two stars, EPIC 201257461 and 201649426 are definitively evolved stars,
with derived radii in excess of 8 \rsun. For approximately one third of the others,
we find the stellar radius posterior distribution to be bimodal, with both main 
sequence and subgiant models of the stars being consistent with the photometric
data.
Future observations to measure the parallaxes of these stars, such as with Gaia,
will be helpful in differentiating between these two models to determine 
more precisely the stellar, and thus the planetary, radii.}

@@

An optical spectrum was obtained using the SuperNova Integral Field Spectrograph
\citep[SNIFS,][]{Aldering02,Lantz04} on the University of Hawai'i
2.2m telescope on the night of January 30 2015.
SNIFS provides simultaneous coverage from 3200\AA--9700\AA\ at a resolution
of $\simeq1000$. Final S/N of the spectrum was $>100$ pre resolving element
in the red ($\sim6000$\AA).
Details of the SNIFS reduction, including dark, bias, and flat-field corrections,
cleaning the data of bad pixels and cosmic rays, and extraction of the
one-dimensional spectrum are described in \citet{Bacon01} and
\citet{Aldering06}.
Flux calibration was performed using a separate pipeline described in \citet{Mann15}.

@@

We combined the derived \teff\ and [Fe/H] values with the empirical
\teff-[Fe/H]-$R_*$ relation from \citet{Mann15} to compute a radius.
Accounting for measurement and calibration errors in [Fe/H] and \teff\ we calculated
a radius 0.394$\pm0.038R_\odot$.
We use these parameters instead of the derived photometric properties for this target.

@@

In \paperit, only parameters directly observable from the \KT\ light curve
itself were reported: the period, time of transit center, and transit depth.
With stellar properties now in hand, we can convert these observational
results into fundamental parameters of each planet candidate.
For each candidate, we fit the light curve using a physical transit model
\citep{Mandel02, Kipping10b} simultaneously with the systematics model
described by \paperit.
We use \texttt{emcee} \citep{Foreman-Mackey12}, an implementation of the
affine-invariant ensemble sampler of \citep{Goodman10}
 to sample from the posterior probability distribution
for the stellar---limb darkening coefficients, mass, radius, and effective
temperature---and planetary---radius, period, phase, impact parameter,
eccentricity, and argument of periapsis---parameters, conditioned on the
light curve and the measured stellar properties.
Following \paperit, the likelihood function that we use is marginalized over
the parameters of the systematics model.
To incorporate the stellar measurements, we approximate the constraints using
a three-dimensional Gaussian in mass, radius, and effective temperature.

In this analysis, we assume the dilution caused by additional stars
contributing flux into the aperture is negligible for nearly all systems.
Given the location of the \Ci\ field at a high galactic latitude, we expect
low contamination by background giants.
Nevertheless, this assumption may not be valid for all systems.
Any contamination unaccounted for, as may happen if any of these stars are
actually unresolved binaries, would cause us to underestimate the radii of any
planets we detect.
Therefore, high-contrast adaptive optics imaging of any systems should be
obtained before any of these planets are placed on a planet mass-radius
diagram.

The planet parameters measured by this analysis are listed in Table 3.

@@

Four of the presented candidates have FPP $>$90\%;
these are considered to be likely false positives.
On the other hand, 24 candidates
have FPP $<$ 1\%.
Two systems, one of which is a planet candidate by the above definition,
 are found to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.
Four of the transit signals might plausibly be caused by
contamination by detected stellar companions within the photometric apertures
(see \S\ref{sec:background}), so we keep these as candidates.

@@

\change{We report these maximum allowable secondary eclipse depths in Table 5.
These values are used by \texttt{vespa} as limits on the allowable secondary eclipse.
Any models that cause a larger event, such as a background eclipsing binary 
consisting of two equal-mass stars in a circular orbit, can be excluded by the data.
We note that with the exception of EPIC 201505350.01, all systems with a maximum
eclipse depth of at least one part per thousand have FPPs of 0.866 or larger.
EPIC 201505350 is a two-planet system with the two planets near a 3:2 period
commensurability, so in this case the ``secondary'' is actually the transits of the 
other planet.}

@@

This research has made use of the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration.

>>>>

\author{%
% The Heavy Lifters
Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
Timothy~D.~Morton\altaffilmark{\princeton},
Daniel~Foreman-Mackey\altaffilmark{\nyu,\cds},
% The Benefactors
John~Asher~Johnson\altaffilmark{\cfa},
David~W.~Hogg\altaffilmark{\nyu,\cds,\mpia},
% The Observers
% (ranked by integration time x collecting area)
Brendan~P.~Bowler\altaffilmark{\caltech,\jcpa},
David~W.~Latham\altaffilmark{\cfa},
Allyson~Bieryla\altaffilmark{\cfa},
Andrew~W.~Mann\altaffilmark{\texas,\hjs},
}

@@

\begin{abstract}
The extended \kep\ mission, \KT, is now providing photometry of new fields every
three months in a search for transiting planets.
In a recent study, Foreman-Mackey and collaborators presented a list of 36 planet
candidates orbiting 31 stars in \KT\ \Ci.
In this contribution, we present stellar and planetary properties for all systems.
We combine ground-based seeing-limited survey data and
adaptive optics imaging with an automated transit analysis scheme to validate
\Nvalidated\ candidates as planets, \Nvalnew\ for the first time,
and identify \Nfp\ candidates as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \change{$2.24 \pm 0.25$ $R_\oplus$} planet with $T_{eq} = 271 \pm 16$ K and an
orbital period of 33 days.
We also present two new open-source software packages which enable this analysis:
\texttt{isochrones}, a flexible tool for fitting theoretical stellar
models to observational data to determine stellar properties, and
\texttt{vespa}, a new general-purpose procedure to calculate false positive probabilities
and statistically validate transiting exoplanets.
\end{abstract}

@@

\section{Introduction}
The \kep\ telescope \citep{Borucki10} has led to a revolution in stellar and planetary
astrophysics, with 7305 ``objects of interest'' and 4173 ``planet candidates''
discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
The fidelity of this sample is high: most of these candidates are truly planets
\citep{Morton11b, Fressin13, Desert15}.
The mechanical failure of two reaction wheels on the spacecraft led to a repurposing
of the spacecraft into the \KT\ mission, in which the telescope points at
fields near the ecliptic plane for $\sim 75$ days at a time \citep{Howell14}.
In this observing strategy, two axes of motion of the spacecraft are
controlled by the two remaining reaction wheels, while the roll of the
spacecraft is balanced with solar radiation pressure and quasiperiodic
thruster firing.
As a result, the detector drifts relative to the sky
at the rate of $\sim 1\arcsec$ hr$^{-1}$, with rapid corrections due to thruster fires
approximately once every six hours.
Over the full duration of each campaign, the targets remain near the
same location on the detector but both the slow drift and the corrections are
observable by eye \citep{Barentsen15}.

@@

\change{During the sampling process, we fit for galactic
extinction as one of our physical parameters.
For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
along that line of sight from the NASA/IPAC Extragalactic Database (NED), which reports the 
\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
COBE/DIRBE and IRAS/ISSA. 
The NED database returns the extinction in all relevant bandpasses except those used by
WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
We include the WISE bandpasses by applying the relative extinction values between 
SDSS, 2MASS, and WISE calculated by \citet{Davenport14}.
In each step of our fitting process, we draw a value for $A_V$, calculate the expected extinction
in all bandpasses $A_X$, and then measure the likelihood of our model stellar fit to the 
observed apparent magnitudes.
We apply a uniform prior ranging from zero to the obtained maximum extinction value and
marginalize over extinction in our final determination of stellar parameters. }

@@

\change{As our stellar results are model-dependent, we caution users who intend to use these 
parameters for other works, such as exoplanet population studies. When available, 
stellar parameters inferred through other techniques such as asteroseismology or 
spectroscopy should supersede these values. 
We note the observed photometric parameters are consistent with spectroscopically-derived
parameters for stars with published spectra, and consistent with typical
model-dependent uncertainties
from photometric data \citep[e.g.][]{Huber14}.
We provide full samples of our posteriors on the physical parameters for each 
star\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}.}

\change{\citet{Bastien14} use observations of stellar ``flicker'' to suggest that 
approximately 50 percent of planet host stars have evolved off the
main sequence onto the subgiant branch, so that both the host stars and their 
planets are larger than previously reported. 
Similarly, in \KT\ \Ci\ we may expect to find evolved stars in a sample of planet
candidates, although we may expect the effect to be lessened due to the 
high galactic latitude of \Ci.
Indeed, we find this to be the case.
Two stars, EPIC 201257461 and 201649426 are definitively evolved stars,
with inferred masses less than 2 \msun but radii above 8 \rsun. 
For approximately one third of the others,
we find the stellar radius posterior distribution to be bimodal, with both main 
sequence and subgiant models of the stars being consistent with the photometric
data.
This number is consistent with our expectations of the number of subgiant 
contaminants in the \Ci\ field (K. Stassun, private communication).
Future observations to measure the parallaxes of these stars, such as with Gaia,
will be helpful in differentiating between these two models to determine 
more precisely the stellar, and thus the planetary, radii.}

@@

An optical spectrum was obtained using the SuperNova Integral Field Spectrograph
\citep[SNIFS,][]{Aldering02,Lantz04} on the University of Hawai'i
2.2m telescope on the night of January 30 2015.
SNIFS provides simultaneous coverage from 3200\AA--9700\AA\ at a resolution
of $\simeq1000$. Final S/N of the spectrum was $>100$ per resolving element
in the red ($\sim6000$\AA).
Details of the SNIFS reduction, including dark, bias, and flat-field corrections,
cleaning the data of bad pixels and cosmic rays, and extraction of the
one-dimensional spectrum are described in \citet{Bacon01} and
\citet{Aldering06}.
Flux calibration was performed using a separate pipeline described in \citet{Mann15}.

@@

We combined the derived \teff\ and [Fe/H] values with the empirical
\teff-[Fe/H]-$R_*$ relation from \citet{Mann15} to compute a radius.
Accounting for measurement and calibration errors in [Fe/H] and \teff\ we calculated
a radius 0.394$\pm0.038R_\odot$.
We use these parameters instead of the derived photometric properties for this target,
although we note the two are consistent at the $1\sigma$ level.

@@

In \paperit, only parameters directly observable from the \KT\ light curve
itself were reported: the period, time of transit center, and transit depth.
With stellar properties now in hand, we can convert these observational
results into fundamental parameters of each planet candidate.
For each candidate, we fit the light curve using a physical transit model
\citep{Mandel02, Kipping10b} simultaneously with the systematics model
described by \paperit.
We use \texttt{emcee} \citep{Foreman-Mackey12}, an implementation of the
affine-invariant ensemble sampler of \citet{Goodman10}
 to sample from the posterior probability distribution
for the stellar---limb darkening coefficients, mass, radius, and effective
temperature---and planetary---radius, period, phase, impact parameter,
eccentricity, and argument of periapsis---parameters, conditioned on the
light curve and the measured stellar properties.
Following \paperit, the likelihood function that we use is marginalized over
the parameters of the systematics model.

In this analysis, we assume the dilution caused by additional stars
contributing flux into the aperture is negligible for nearly all systems.
Given the location of the \Ci\ field at a high galactic latitude, we expect
low contamination by background giants.
Nevertheless, this assumption may not be valid for all systems.
Any contamination unaccounted for, as may happen if any of these stars are
actually unresolved binaries, would cause us to underestimate the radii of any
planets we detect.
Therefore, high-contrast adaptive optics imaging of any systems should be
obtained before these planets are used in population inference studies.
The planet parameters measured by this analysis are listed in Table 3.

@@

Six of the presented candidates have FPP $>$90\%;
these are considered to be likely false positives.
On the other hand, 24 candidates
have FPP $<$ 1\%.
Two systems, one of which is a planet candidate by the above definition,
 are found to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.
Four of the transit signals might plausibly be caused by
contamination by detected stellar companions within the photometric apertures
(see \S\ref{sec:background}), so we keep these as candidates.

@@

\change{We report these maximum allowable secondary eclipse depths in Table 5.
These values are used by \texttt{vespa} as limits on the allowable secondary eclipse.
Any models that cause a larger event, such as a background eclipsing binary 
consisting of two equal-mass stars in a circular orbit, can be excluded by the data.
We note that with the exception of EPIC 201505350.01, all systems with a maximum
eclipse depth of at least one part per thousand have FPPs of 0.866 or larger.
The exception, EPIC 201505350, is a two-planet system with the two planets near a 3:2 period
commensurability, so in this case the ``secondary'' is actually the transits of the 
other planet.}

@@

\change{This research has made use of the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration.}
